master thesis

### 2018-01-19 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - random binary tree; tag tree

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}
  \section{Simulation}
    \begin{itemize}
      \item build random binary trees, tag these (parameters: parasites vs free-living, beta-distribution)
      \item run fitch-parsimony, wagner-parsimony, our parsimony like algorithm
      \item build not binary tree (poisson distribution?)
      \item run new algorithms
      \item compare trees (distances)
    \end{itemize}
  \section{Implementation}
\chapter{Results}
\chapter{Discussion}

  Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit Information. \\
  Simulation von subtrees \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------------------
\bibliography{bibliographie}
\bibliographystyle{alphadin}

>>>>

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}

  This work consist of two aspects. One is the application of the algorithm to our question

  Diese Arbeit besteht aus zwei Fragestellungen
  gute Algorithmen zu finden und sie auf unser Anwendungsbeispiel anzuwenden.

  Zur Bewertung der gefundenen / entwickelten algorithmen haben wir eine Simulation ausgeführt.

  Auf der Anderen Seite haben wir unser reales Problem aufgestellt, für die Algorithmen vorbereitet und 
  diese angewendet.

  Metadata -> Simulation ->  real Data

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Metadata analysis}
    Properties of real Data - Metadata analysis

    There are some Parameters to find out or notice:
    \begin{itemize}
      \item transition probabilities of tags
      \item multifurcation
      \item nr of parasites to free-living
      \item nr of unknown nodes 
    \end{itemize}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Simulation}
    \begin{itemize}
      \item build random binary trees, tag these (parameters: parasites vs free-living, 
        beta-distribution)
      \item run fitch-parsimony, wagner-parsimony, our parsimony like algorithm
      \item build not binary tree (poisson distribution?)
      \item run new algorithms
      \item compare trees (distances)
    \end{itemize}

    \begin{enumerate}
      \item build random binary trees
      \item tag tree
      \item multifurcate tree
      \item run maximum parsimony algorithms
      \begin{itemize}
        \item Fitch
        \item Sankoff (Castor package)
        \item my algorithm
      \end{itemize}
      \item Evaluation
    \end{enumerate}

    %---------------------------------------------------------------------------------------------------
    \subsection{random binary tree}
      To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
        function which returns a BaseTree \footnote{
          https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py
        }:
      \begin{lstlisting}
        from Bio import Phylo
        Phylo.BaseTree.Tree.randomized(number_leafnodes)
      \end{lstlisting}
      From the BaseTree class:
      \begin{lstlisting}
        def randomized(cls, taxa, branch_length=1.0, 
              branch_stdev=None):
        """Create a randomized bifurcating tree given a list
              of taxa.
          :param taxa: Either an integer specifying the number
              of taxa to create (automatically named taxon#), 
              or an iterable of taxon names, as strings.
          :returns: a tree of the same type as this class.
        """
      \end{lstlisting}
      \todo{Zitat von BaseTree und buildTree.py}

    %---------------------------------------------------------------------------------------------------
    \subsection{tag tree}
      At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
        data.\\
      Let's say the first specie (the root node) was free-living (start with a parasite without a host 
        makes no sence). For every transition from a node to his child, we take a random number from
        the father distribution. We decided that from the biological perspective a beta distribution
        reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
        For example when our father node was free-living, then we take from the free-living beta
        distribution. Is the number under the threshold for beeing parasite, we get a change and tag
        the current node as parasite. Otherwise we tag it as free-living. \\
        With this procedure we traverse through the tree from the root to every leave node. A part of
        this code you see here:
      \begin{lstlisting}
        from numpy import random
        if father_tag == 0:
          # freeliving_distribution:
          new_random = random.beta(a=A_FL, b=B_FL)
        else:
          # parasite_distribution:
          new_random = random.beta(a=A_P, b=B_P)
        tag = 0         # -> FL
        if new_random < percentage_parasites:
          tag = 1       # -> P
      \end{lstlisting}
      \begin{figure}
        \caption{60\% Free-living - 40\% Parasites}
        \centering
          \includegraphics[width=0.5\textwidth]{Figures/40-60.png}
      \end{figure}
      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold}

      unknowns.. forget information.. nodelist

    %---------------------------------------------------------------------------------------------------
    \subsection{multifurcate tree}
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{real data analysis}
    \begin{itemize}
      \item Import tree
      \item Import interactions
      \item run castor algorithm / and others?
      \item interprete results (leave one out)
    \end{itemize}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Implementation}

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Results}

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Discussion}
  Wie gut ist der randomisiert erstellte Baum? \\
  Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
  Information. \\
  Simulation von subtrees \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\

@@

  Selecting of the 'right'  / best Distribution

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\bibliography{bibliographie}
\bibliographystyle{alphadin}
